### 2016-06-30 related-work.tex
edits

\paragraph{Reasoning under weak isolation} In~\cite{feketessi}, Fekete
\emph{et al.} propose a theory to characterize non-serializable executions
that arise under {\sc si}. Fekete~\cite{fekete2005} also proposes an
algorithm that allocates either {\sc si} or {\sc ser} isolation levels
to transactions while guaranteeing the serializability of the
execution. In~\cite{gotsmanpodc16}, Cerone et al. improve on Adya's
{\sc si} specification and use it to derive a static analysis that
determines the safety of substituting {\sc si} with a weaker variant
called \iso{Parallel Snapshot Isolation}~\cite{psi}. All of them focus
on establishing the equivalence of executions between a pair of
isolation levels, without taking application invariants into account.
Bernstein et al.~\cite{bern2000} propose informal semantic conditions
to ensure the satisfaction of application invariants under weaker
isolation levels.  However, no formal proof system has been proposed.
Furthermore, all the aforementioned approaches are tailor-made for a
finite set of well-understood isolation levels (rooted
in~\cite{berenson}) under a pre-defined consistency model (usually
{\sc sc}).

@@

\paragraph{Reasoning under relaxed memory} Considering the
correspondences between axiomatic models of relaxed
memory~\cite{battycpp} and weakly consistent
replication~\cite{burckhardt14}, it is reasonable to expect similar
reasoning approaches to work in both the cases. Ridge~\cite{rgtso}
generalizes rely-guarantee reasoning to the x86-TSO memory model.
Likewise, Vafeadis \emph{et al.}~\cite{rsl13} generalize concurrent
separation logic (CSL)~\cite{csl} to the C11 relaxed memory model.
Ferreira et al.~\cite{ferreira10} propose a parameterized operational
semantics for relaxed memory models, but the parameterization is over
a relation between relaxed memory programs and related {\sc sc}
programs. They also prove the soundness of CSL for the weakest memory
model expressible in their semantics, but neither a parameterized (in
the aforementioned sense) CSL, nor a CSL specialized for any relaxed
memory model is proposed. In fact, to the best of our knowledge, there
does not exist a proof system that combines axiomatic semantics of
memory models and operational semantics of programs in a unified
reasoning framework.  \SJ{cite plan b: a buffered memory model for Java.}

>>>>

\paragraph{Reasoning under weak isolation} In~\cite{feketessi}, Fekete
\emph{et al.} propose a theory to characterize non-serializable executions
that arise under {\sc si}. Fekete~\cite{fekete2005} also proposes an
algorithm that allocates either {\sc si} or {\sc ser} isolation levels
to transactions while guaranteeing the serializability of the
execution. In~\cite{gotsmanpodc16}, Cerone \emph{et al.} improve on Adya's
{\sc si} specification and use it to derive a static analysis that
determines the safety of substituting {\sc si} with a weaker variant
called \iso{Parallel Snapshot Isolation}~\cite{psi}. All of them focus
on establishing the equivalence of executions between a pair of
isolation levels, without taking application invariants into account.
Bernstein \emph{et al.}~\cite{bern2000} propose informal semantic conditions
to ensure the satisfaction of application invariants under weaker
isolation levels.  However, no formal proof system has been proposed.
Furthermore, all the aforementioned approaches are tailor-made for a
finite set of well-understood isolation levels (rooted
in~\cite{berenson}) under a pre-defined consistency model (usually
{\sc sc}).

@@

\paragraph{Reasoning under relaxed memory} Considering the
correspondences between axiomatic models of relaxed
memory~\cite{battycpp} and weakly consistent
replication~\cite{burckhardt14}, it is reasonable to expect similar
reasoning approaches to work in both the cases. Ridge~\cite{rgtso}
generalizes rely-guarantee reasoning to the x86-TSO memory model.
Likewise, Vafeadis \emph{et al.}~\cite{rsl13} generalize concurrent
separation logic (CSL)~\cite{csl} to the C11 relaxed memory model.
Ferreira \emph{et al.}~\cite{ferreira10} propose a parameterized
operational semantics for relaxed memory models, but the
parameterization is over a relation between relaxed memory programs
and related {\sc sc} programs. They also prove the soundness of CSL
for the weakest memory model expressible in their semantics, but
neither a parameterized (in the aforementioned sense) CSL, nor a CSL
specialized for any relaxed memory model is proposed.  ~\cite{DLZ+13}
presents a \emph{buffered memory model} for Java that deines an
axiomatic definition for the JMM in terms of memory reorderings, and
an operational instantiation consistent with the total store ordering
(TSO) memory model found on x86 processors, and demonstrates the
equivalence of the two definitions.  However, there is no attempt to
parameterize the model over different reordering or consistency
definitions as we demonstrate here.
